\textbf{How to measure maximally precise radial velocities from a set of spectra:\\ The time-independent spectrum case}

### 2019-08-08 paper/paper.tex
deletion
tweak

While the general idea of measuring a Doppler shift by the relative
motions of stellar absorption lines is fairly straightforward, there
are considerable complexities and subtleties.
These start at the design of the spectrograph hardware itself
and then go on to include 
the observing strategy, calibration methodology, spectral extraction,
choice of reference spectrum or template, and treatment of telluric absorption
features.
Here we will focus on the last parts of this: We will presume that the
spectrograph is delivering wavelength-calibrated, extracted, continuum-normalized
spectra with minimal issues, and we will consider how to obtain the most
precise possible \RV\ measurements from those good spectra.
A more complete treatment would consider the hardware, observing strategy,
calibration methodology, spectral extraction, and \RV\ measurement as
an integrated system of hardware, software, and operations.
That's an important direction for future research, but out of scope for this \documentname.

@@

Our primary aim in this work is to establish a common frame of reference for these methods based on their relative ability to extract maximum-precision RVs and their robustness in the face of various expected structured noise sources.

>>>>

While the general idea of measuring a Doppler shift by the relative
motions of stellar absorption lines is fairly straightforward, there
are considerable complexities and subtleties.
These start at the design of the spectrograph hardware itself
and then go on to include 
the observing strategy, calibration methodology, spectral extraction,
choice of reference spectrum or template, and treatment of telluric absorption
features.
Here we will focus on the last parts of this: We will presume that the
spectrograph is delivering wavelength-calibrated, extracted, continuum-normalized
spectra with minimal issues.
We will consider how to obtain the most
precise possible \RV\ measurements from those good spectra.
A more complete treatment would consider the hardware, observing strategy,
calibration methodology, spectral extraction, and \RV\ measurement as
an integrated system of hardware, software, and operations.
That's an important direction for future research, but out of scope for this \documentname.

@@
